Identification and Spatial Analysis of Russian Law Firms Naming Using Text Embeddings

### 2025-01-25 law-firms-names/Paper.Rmd
Edit methods, #4

---
title: "Discovering and Analysing Spatial Heterogenity in Russian Law Firms Naming Using Text Embeddings"
author: "Pavel Syomin"
output:
  word_document:
    reference_doc: "journal-article/reference.docx"
bibliography: "journal-article/refs.bib"
csl: "journal-article/apa.csl"
link-bibliography: False  
---

@@

### 2.2.4. Settlement embeddings

The embeddings of firm names are grouped by settlement and averaged. In this paper, these average vectors are referred to as settlement embeddings or settlement vectors. Each vector represents the combined meaning associated with the names of law firm names within a specific settlement. The mathematical similarity of settlement vectors is analogous to the similarity of law firm names in settlements. Settlement embeddings were introduced to reduce computational complexity of working with individual vectors. Multiple law firms may be located in the same settlement, and with the absence of within-city variation, it is possible to treat their names vectors as a single object.

### 2.2.5. Naming strategies identification

@@

Each group except for the “Misc” category represents a specific naming strategy. The “Form” strategy encompasses names that are based on a word or words denoting a kind of business entity, including “company”, “firm”, “group”, “partnership”, “center”, “alliance”, and “corporation”. The “Law” strategy emphasizes the firm's affiliation with the legal services market, employing terms such as “legal”, “juridical”, “lex”, “law”, and “lawyer”. Names belonging to the “Service” strategy may indicate a particular service provided by a law firm (“advisor”, “consulting”, “protection”, “support”, “warrant”), describe the sectors of businesses the firm is primarily engaged with (“technology”, “development”, “house management”, “accounting”), or mention services in general. The “Misc” category is a catch-all group for names that do not clearly align with any other category.

### 2.2.6. Analysis of firm names similarity

The similarity of law firm names between regions is calculated as a Euclidean distance between the corresponding region vectors. Henceforth, this will be referred to as a semantic distance between regions. A neighborhood of regions is determined on the basis of the existence of a common border between them, thus allowing for two regions to either be neighboring or not. A geographic distance between regions is calculated as a linear distance between the centroids of the region polygons. To provide a proxy of economic links between regions, the belonging to the same economic region is utilized. According to @Leyzerovich2010, Russia is comprised of 11 economic regions, which themselves consist of a number of regions. The defining characteristics of an economic region are its internal unity, distinction from the other economic regions, and the economic links that exist between constituting regions, cities, and enterprises within them.

To estimate the effect of neighboring, regions are divided into pairs of neighbors and non-neighbors. Semantic distances are then calculated between the regions in each pair within the two groups. A median semantic distance is calculated for each group. It is expected that the median semantic distance between neighboring regions would be less than that between regions that do not share a border.

A similar technique is used to ascertain whether geographical distance impacts semantic distance. Pairwise semantic and geographical distances between all regions are calculated, and the correlation between geographical distance and semantic distance is estimated. It is expected that the coefficient of correlation will be positive.

To analyze the role of economic links, the pairwise semantic distances between regions are split into two groups: distances between regions within an economic region (within-distances) and distances between regions belonging to an economic region and all the other regions (outside-distances). The median of both within-distances and outside-distances is calculated for each economic region. It is expected that semantic distances between regions within an economic region would be smaller than those between regions belonging to different economic regions.

### 2.2.7. Analysis of naming strategies

A dominant naming strategy is ascribed to each region, defined as the naming strategy used by the majority number of law firms within that region. Dominant naming strategies are then mapped and analyzed visually to ascertain whether any geographical patterns emerge. In addition, the boundaries of economic regions are illustrated on the same map, and the dominant naming strategies of regions within each economic region are examined. No a priori hypotheses are formulated regarding the geographical patterns. As for naming strategies within economic regions, it is expected that they will be similar.

>>>>

---
title: "Identification and Spatial Analysis of Russian Law Firms Naming Using Text Embeddings"
author: "Pavel Syomin"
output:
  word_document:
    reference_doc: "journal-article/reference.docx"
bibliography: "journal-article/refs.bib"
csl: "journal-article/apa.csl"
link-bibliography: False  
---

@@

### 2.2.4. Naming strategies identification

@@

### 2.2.5. Spatial regularities identification

Analysis of autocorrelation is used to check whether the spatial distribution of names belonging to each cluster identified on the previous step is random or has some regularities. Regions (constituent entries) or the Russian Federation were selected as a spatial subdivision for calculating the autocorrelation measures. It could have been more reasonable to use the next spatial level, municipal territories, to perform the computations, but exploratory data analysis has shown that a lion's share of such territories has no law firms, because the legal business is highly concentrated in cities and large settlements.

The autocorrelation analysis has two branches differing in the way the spatial weights matrix is constructed. In the first branch, neighborhood of the regions is defined based on the adjacency of region's polygons. Sakhalin and Kaliningrad regions, being enclaves and thus having zero immediate neighbors, were manually connected with a few closest regions. In the second branch, the neighborhood of the regions was identified based on their belonging to the same economic region according to the classification widely used by economic geographers and spatial development practitioners in Russia for decades and outlined, for example, in [@Leyzerovich2010]. All regions within the same economic region are considered to be connected, and all regions of the different economic regions are disconnected, resulting in spatial weights graph comprised of several independent components. Despite the fact that the concept of economic regions in Russia is sometimes considered legacy, it is still implicitly used by researchers and practitioners, and the belonging to the same economic regions implies economic linkage, similarity and cooperation of regions. Thus, it makes sense to utilize this classification.

For each cluster, a global Moran's I metric is calculated. The variable of interest is a share of law firm names belonging to the cluster in a total quantity of law firm names in a region. If there are no law firm names of the cluster in the region, the share is considered to equal zero. P-values are adjusted for multiple comparisons with Holm's correction. Significance level (alpha) is set to 0.05.

For the clusters with statistically significant global Moran's I, a local Moran's I was subsequently calculated. P-values are adjusted with local Holm's correction. Cluster classification of local Moran's I are mapped.
